---
title: "Math4753 Package Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Math4753 Package Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Math4753Alls0003)
```

# MATH4753 Package Functions

## myddt

myddt returns the data frame, the relative frequency of a chosen parameter, the subset data frame, and a scatter plot of the data with a quadratic model. 
```{r}
library(Intro2R)
myddt(df=ddt, species="CCATFISH")
```

## myncurve

myncurve returns a normal distribution curve with the area shaded between the curve and the x-axis from -10000 to x=a. The area of P(x<=a) is also displayed on the plot.

```{r}
myncurve(mu=10, sigma=2, a=8)
```

## scatterhist

scatterhist returns a scatter plot with the chosen x and y parameters of a given data set. Also, histograms for both parameter are shown outside of the scatter plot.

```{r}
{with(ddt, scatterhist(LENGTH,WEIGHT, xlab="Length", ylab="Weight"))}
```

## mynbin

mynbin returns the negative binomial probability that there are y number of failures before the rth success.

```{r}
mynbin(y=10,r=3,p=0.4)
```
